On the Dynamics of Anthropomorphism in Robotics \thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}

### 2013-05-21 anthropomorphism.tex
new paragraph to introduce our model

We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature.  We rather suggest to understand anthropomorphism in HRI as a dynamic, and context-dependent process, which is likely to change over time and with growing user experience with the robot (which we assume comes along with a familiarization and better understanding of the robot). This viewpoint considers the so called \textit{novelty effect} which has been observed during long-term studies with innovative technologies and robots. In the following, we present our understanding of the dynamics of anthropomorphism and try to model this process as a function of time and growing experience.

>>>>

We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature that once observed during a short-term interaction reflects a sustaining social effect. So far, the HRI community has not investigated how anthropomorphism in human-robot interactions evolves over time (during the process of adopting a robot, for instance). However, based on an extensive literature review and our own work, we believe that the social phenomenon will not always be the same but evolve over time, with growing interaction and experience with the robot. We would like to present an extension to the understanding of anthropomorphism in HRI which takes time / interaction / experience / familiarization into account. Consequently, we suggest to understand anthropomorphism in HRI as a dynamic process, which is likely to change over time and with growing user experience with the robot (which we assume comes along with a familiarization and better understanding of the robot). This viewpoint also considers the so called \textit{novelty effect} which has been observed during long-term studies with innovative technologies and robots. In the following, we present our understanding of the dynamics of anthropomorphism and try to model this process as a function of time and growing experience (see Figure \ref{fig:dynamics}).
